I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-11 Paper/Paper_noProof.tex
Add files via upload
fix bug
milp fixed
section 3

At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction \cite{MILP}, which is a priori a complete method (but whose complete encoding is much slower). 
Consider an unstable neuron $y \in[\alpha,\beta]$. The value of $\ReLU(y)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in ${0,1}$, using 4 constraints:
\vspace{-0.1cm}
\begin{align*}
	\hat{y} \leq y \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \geq y-\alpha \cdot (1-a)
\end{align*}

@@

As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
We state here and prove later that the LP abstraction is strictly more accurate than the DeepPoly abstraction. It actually corresponds to consider in DeepPoly both linear functions lower bounding the ReLU function, $ReLU{y} \geq 0$ and $ReLU{y} \geq y$, while DeepPoly consider exactly one.

\begin{theorem}
 Given $y \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints are equivalent:
 \vspace{-0.1cm}
 \begin{align*}
	 \hat{y} \leq y \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad & \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \geq y-\alpha \cdot (1-a), a \in [0,1] \\
	 \text{and} \quad \hat{y} \geq 0 \quad & \wedge \quad \hat{y} \geq y \quad \wedge \quad \hat{y} \leq \beta \frac{y-\alpha}{\beta-\alpha}
\end{align*}

\end{theorem}

@@

\section{Compensate, Diamond and Node Chosen}

In this section, we will explore the key factor for the loss of accuracy in our LP/MILP models: \emph{compensating pair}. And we will develop a process of open node chosen by the principle of \emph{Compensating Pairs}.

\subsection{Compensating pair}

@@

\begin{tikzpicture}
	\node[circle, draw= purple, thick, minimum width = 20,
	minimum height = 20] (input1) {$a$};

@@

	\draw[->,thick,draw= red] (hidden3) -- (output)node[midway, below] {$1$};
	\draw[->,thick,draw= green] (hidden4) -- (output)node[midway, below] {$1$};
\end{tikzpicture}

>>>>

At the other end of the spectrum, we find the Mixed Integer Linear Programming (MILP) value abstraction \cite{MILP}, which is a priori a complete method (but whose complete encoding is much slower). 
Consider an unstable neuron $y \in[\alpha,\beta]$. The value of $\ReLU(y)$ can be encoded exactly in an MILP formula with one integer (actually even binary) variable $a$ valued in ${0,1}$, using 4 constraints:
\vspace{-0.1cm}
\begin{align*}
	\hat{y} \geq y \quad \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad \wedge \quad \hat{y} \leq y-\alpha \cdot (1-a)
\end{align*}

@@

As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
We prove now that the LP abstraction is strictly more accurate than the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(y) \geq 0$ and $ReLU(y) \geq y$, while DeepPoly considers exactly one.

\begin{proposition}
	\label{LP}
 Given $y \in [\alpha,\beta]$ with $\alpha < 0 < \beta$, the following two systems of constraints 
 1) for LP and 2) for DeepPoly with both lower bounds are equivalent:
 \vspace{-0.3cm}
 \begin{align*}
	 & 1) \quad \hat{y} \geq y \quad \wedge \quad \hat{y} \geq 0, \quad \wedge \quad \hat{y} \leq \beta \cdot a \quad \wedge \quad \hat{y} \leq y-\alpha \cdot (1-a), \, a \in [0,1] \\
	 \text{and} \quad  & 2)  \quad \hat{y} \geq y \quad \wedge \quad \hat{y} \geq 0 \quad \wedge \quad \hat{y} \leq \beta \frac{y-\alpha}{\beta-\alpha}
\end{align*} 
\end{proposition}

\begin{proof}
Obviously, the 2 lower bound constraints are the same in 1) and 2).

It remains to prove that the 2 upper bound contraints of 1) LP corresponds to the 2) DeepPoly linear upper bound. For that, we study the upper bound function in the variable $a \in  [0,1]$, with $y \in [\alpha,\beta]$ fixed. We have $\hat{y}$ in 1) upper bounded by $max_{a \in [0,1]} (min(\beta \cdot a, y - \alpha (1-a)))$, and this bound can be reached. 
The function $min(\beta \cdot a, y - \alpha (1-a))$ reaches its maximum for 
$\beta \cdot a = y - \alpha (1-a)$, that is 
$(\beta - \alpha) a = y - \alpha$, i.e. 
$$ a = \frac{y - \alpha}{\beta-\alpha}$$

It thus gives an upper bound at 
$\beta \cdot a = \beta \frac{y - \alpha}{\beta-\alpha}$, which is exactly the function used in DeepPoly.
\qed
\end{proof}

@@

\section{Compensating pair of paths}

In this section, we explore the key factor for the loss of accuracy in value abstraction methodologies, as those we presented before (except for full MILP which is exact but too costly). 
Namely, we uncover that \emph{compensating pair of paths} are the reason for the loss of precision.

@@

\begin{figure}
\centering
\begin{tikzpicture}

	\node[circle, draw= purple, thick, minimum width = 20,
	minimum height = 20] (input1) {$a$};

@@

	\draw[->,thick,draw= red] (hidden3) -- (output)node[midway, below] {$1$};
	\draw[->,thick,draw= green] (hidden4) -- (output)node[midway, below] {$1$};
\end{tikzpicture}
\end{figure}
